\documentclass[a4paper,4pt]{article}
\usepackage[a4paper,margin=0.8in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\pagenumbering{gobble}

% Spacing
\setlength{\parskip}{0.2em}
\setlength{\parindent}{2pt}
\setlist[itemize]{topsep=0pt, itemsep=1pt, left=0pt}

% Section style
\titleformat{\section}{\Large\bfseries\color{black}}{}{0em}{}[\titlerule]

\begin{document}

% --- Header ---
\begin{center}
    {\Large \textbf{Arjan Singh Hayre}} \\
    London, UK • \href{mailto:arjanh6@gmail.com}{arjanh6@gmail.com} • 07360 185965 \\
    GitHub: \href{https://github.com/The-Asgardian}{The-Asgardian} • LinkedIn: \href{https://www.linkedin.com/in/arjan-hayre-aa406319b/}{arjan-hayre}
\end{center}



% --- Profile ---
\section*{Profile}
Full-stack and backend engineer with experience in distributed systems, microservices, and applied machine learning. Delivered production workflows, backend services, and real-time data tools across multiple internships. Strong grounding in C++ systems programming through academic projects involving concurrency, memory management, and low-level optimisation.


% --- Education ---
\section*{Education}
\textbf{Imperial College London}, UK \\
MEng/BEng Electronics and Information Engineering (Predicted Upper second class) \hfill 2022--2026 \\
A-Levels: Mathematics (A*), Physics (A*), Further Mathematics (A)

% --- Experience ---
\section*{Experience}

\textbf{Full-Stack Developer} — Summer Internship \hfill Jul 2024 -- Oct 2024 \\
\emph{Xcceler8 Ltd (Client: WeBook), Remote}  
\begin{itemize}
    \item Built booking and reservation workflows using Camunda BPMN and Spring Boot microservices; supported a service handling on the order of \emph{hundreds of thousands of HTTP requests per day}, improving system reliability and cutting down manual corrections in production.  
    \item Designed PostgreSQL schemas and introduced Redis caching for high-traffic endpoints, cutting median API response time from roughly 180\,ms to 95\,ms under peak load. 
    \item Extended API gateway to enforce rate limiting and request validation, enabling the system to sustain bursts of concurrent requests with minimal failures.  
    \item Collaborated with product, UX and QA teams to ship regular feature releases, helping shorten release cycles and maintain consistent throughput of new deployments.  
\end{itemize}

\textbf{Full-Stack Developer} — Summer Internship \hfill Jul 2023 -- Oct 2023 \\
\emph{Xcceler8 Ltd, London}  
\begin{itemize}
    \item Integrated Firebase Authentication and Firestore with backend services, implementing OAuth2/JWT authentication flows — improved user login stability across thousands of daily users.  
    \item Developed RBAC (role-based access control) and access-control modules across services, tightening security and reducing the incidence of permission-related errors.  
    \item Built internal admin dashboard components using React and Material UI; enabled support teams to manage user accounts and data queries more efficiently, reducing support-render time per request.  
\end{itemize}

\textbf{Backend Developer} — Summer Internship \hfill Jul 2022 -- Oct 2022 \\
\emph{Dorchester Homes, London}  
\begin{itemize}
    \item Built a property-valuation assistant using Python regression models on historical sales data.
    \item Implemented a project-tracking and VAT automation dashboard used by operations staff weekly, streamlining internal reporting and eliminating multiple manual steps from monthly financial workflows.  
    \item Optimised SQLite schema and queries — improved average report generation time from ~2.1 seconds down to ~0.7 seconds under typical load.  
\end{itemize}



% --- Skills ---
\section*{Technical Skills}
\textbf{Languages:} C++, Python, JavaScript/TypeScript, Go
\textbf{Frameworks:} React, Node.js, Flask, Spring Boot \\
\textbf{Systems:} Microservices, Kafka, Redis, Docker, REST 
\textbf{Databases:} PostgreSQL, MongoDB, SQLite 
\textbf{ML/AI:} PyTorch, TensorFlow, LLM tooling (RAG, LoRA, llama.cpp) 
\textbf{Security:} OAuth2, JWT, RBAC, bcrypt, security headers, rate limiting 
\textbf{Tools:} Wireshark, OWASP ZAP, nmap, Fail2ban

\end{document}
